%\title{My CV}
%

\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{fontawesome}

\begin{document}

\part{Vipul Sharma}

\section{Work experience}

\begin{eventlist}

\item{August 2018 -- Present}
     {Member, Programming Club}
     {\href{https://www.facebook.com/prog.iitmandi/}{Programming Club, IIT Mandi}}

Maintaining programming club related activities around the campus. Conducting workshops for freshers related to development and competitive programming.

\item{June 2018 -- September 2018}
     {WebD Coordinator, Rann-neeti IIT Mandi}
     {\href{http://www.rann-neeti.co/}{Rann-neeti, IIT Mandi}}

I was the web development coordinator in the official sports fest of IIT Mandi - Rann-neeti. Managed registrations, online schedules and design during this period.

\end{eventlist}

\section{Projects}

\begin{eventlist}

\item{July 2018}
	{HTML/CSS, MySQL, PHP}
    {\href{https://github.com/vsvipul/Rann-Neeti-2018}{Rann-neeti 2018}}

Website for Rann-neeti 2018, which is the official sports fest of IIT Mandi.

\item{October 2018}
     {Python/Django, HTML/CSS}
     {\href{https://github.com/vsvipul/Car-Pool}{CarPool}}

A car pool system created for STAC Hackweek 2018. It is made keeping in mind the problem of transportation when you have to reach Mandi from campus or vice vers for some work and the bus timings are not favourable. Someone might also be going to the same location using his/her personal vehicle and is willing to help, can use this app.

\item{November 2018}
     {Javascript/jQuery, Github API, HTML/CSS}
     {\href{https://github.com/vsvipul/GithubUnfollowers}{GithubUnfollowers}}


GithubUnfollowers is a JavaScript webapp. It gives an easy way to list all those people who don't follow you back on Github. {\href{https://vsvipul.github.io/GithubUnfollowers/}{See demo}}

\end{eventlist}

\personal
    [linkedin.com/in/vsvipul/]
   	{vsvipul.github.io}
    {b17069@students.iitmandi.ac.in}
    {github.com/vsvipul}

\section{Education}

\begin{yearlist}

\item[B.Tech Computer Science and Engineering]{2017-present}
     {B.Tech in Computer Science and Engineering}
     {\large{IIT Mandi} \newline CGPA -- 8.66/10 (2 Semesters)}

\item{2015 -- 2016}
     {Class 12th CBSE}
     {Aadhunik Public School, Sidhbhari, Dharamshala, Percentage -- 95.6 \%}

\item{2013 -- 2014}
     {Class 10th CBSE}
     {Aadhunik Public School, Sidhbhari, Dharamshala, CGPA -- 10/10}

\end{yearlist}

%\section{Positions of Responsibility}

%\begin{yearlist}

%\item{2017}
 %    {Coordinator}
  %   {Event Conduction, Technozion, Technical festival, NITW}

%\item{2016-17}
%     {Assistant Manager}
%     {IG MakerSpace Student Team, NITW}

%\item{2015-16}
%     {Sub Co-ordinator}
%     {Springspree, Cultural Festival, NITW}

%\item{2015-16}
%     {Class Representative - Elected}
%     {Students Council, NITW}

%\end{yearlist}

\section{Skills \& Interests}

\begin{factlist}

\item{Programming}
     {C, C++, HTML5 \& CSS, JS, PHP}

\item{Technology Stack}
	{SQL}

\item{Tools}
     {Git, Heroku, Github, Linux}

%\item{Others}
%    {Basic-OS, Computer Architecture and Networks, Agile, DevOps}

\end{factlist}

%\section{Courses Undertaken}

%\begin{factlist}


%\end{factlist}

\end{document}
